---
title: "Confirmatory Factor Analysis"
author: "Harlan A Nelson"
---

## Latent Variables

Characteristics

:   Not Directly Measured

:   Computed from the measured variables

:   

contrasted to:

:   manifest variables

:   observed variables

instrument

:   inventory

scale score

Used in:

-   Predictions in Multiple Regression

-   Canonical Correlation Analysis

-   Factors in Factor Analysis

Model

:   delineates ties of a latent variable with a set of measured variables and other latent variables

:   Mathematical expression of a theoretical construct

:   describe the fit of a model to data. Test proposed structure

Confirmatory factor analysis

:   Test a hypothesized correlation structure

:   Test a hypothesised relation between factors and measured variables.

:   Start with an hypothesized factor structure, calculate the fit.

:   Associate each variable (item) with only one factor

:   Different causal framework

:   requires specialized software (Amos)

:   assess the association of a set of variable with a single factor

:   assess the structure of multiple factors simultaneously in a model

:   structural equation model SEM.

:   Measurement Model

**Parts of the confirmatory factor analysis model**

-   Measured variables Rectangles. (observed variables, indicator variables)
-   Latent factors: rounde d
-   Error terms: unique variables, residuals, disturbances.
    -   associated with predicted variables
    -   endogenous variables
    -   The part of the indicators variance that is not shared with the factor.\
    -   latent
-   Paths
    -   one directional: causality
    -   two direction: correlation
    -   estimated by a path coefficient
    -   pattern coeffiient from factor to indicator, beta weights
-   Parameter estimates

**Types of objects**

```{r}
dat <- read.csv("https://stats.idre.ucla.edu/wp-content/uploads/2021/02/worland5.csv")
```

```{r}
install.packages('pacman')
pacman::p_load(lavaan, tidyverse)
```

```{r}
dat
```

```{r}
cov(dat)
```

```{r}
#simple regression using lm()
m1a <- lm(read ~ motiv, data=dat)
(fit1a <-summary(m1a))
```

-   square: measured variabls
-   round: latent variables
-   error variable: also a latent variable
