---
title: "Python Decorators and R Equivalents"
author: "Grok 2"
date: "2025-02-03"
format:
  html:
    code-fold: true
    code-tools: true
---

# Python Decorators and R Equivalents
## Introduction
## Python Decorators
### Basic Example of a Decorator

```{python}
def my_decorator(func):
    def wrapper():
        print("Something is happening before the function is called.")
        func()
        print("Something is happening after the function is called.")
    return wrapper

@my_decorator
def say_hello():
    print("hello!")

say_hello()
```
While Python decorators provide a clean and elegant way to modify function behavior, R offers different but equally potent methods through closures and OOP features like method chaining. Both approaches allow developers to extend function capabilities dynamically, enhancing code readability and maintainability.


3. R Equivalents
R doesn't have decorators in the Python sense, but you can achieve similar results with:

```{r}
say_hello <- function() {
  cat("Hello!\n")
}

decorated_say_hello <- decorate_with_log(say_hello)
decorated_say_hello()

```

Explanation:
decorate_with_log wraps another function, adding logging before and after the function call.

Method Chaining in R
R's object-oriented programming can mimic decorator behavior through method chains:

```{r}
Person <- R6::R6Class(
  "Person",
  public = list(
    name = NULL,
    initialize = function(name) {
      self$name <- name
    },
    greet = function() {
      cat(paste("Hello,", self$name, "\n"))
      invisible(self)
    },
    twice = function() {
      self$greet()
      self$greet()
      invisible(self)
    }
  )
)

person <- Person$new("Bob")
person$greet()$twice()

```

Explanation:
Here, greet() and twice() are method calls that can be chained to mimic decorator behavior.

4. Conclusion
While Python decorators provide a clean and elegant way to modify function behavior, R offers different but equally potent methods through closures and OOP features like method chaining. Both approaches allow developers to extend function capabilities dynamically, enhancing code readability and maintainability.
